Lifting CDCL to Relational Domains

### 2016-10-15 domains.tex
meet decomposition

\begin{definition}{(Meet Irreducible)} A \emph{meet irreducible} $m$ 
in a complete lattice structure $A$ is an element with the following property.
\[\forall m_1, m_2 \in A: m_1 \meet m_2 = m \implies (m = m_1 \lor m = m_2), m \neq \top \]  
\end{definition}

@@

\begin{definition}{(Complementable Meet Irreducible)} 
A meet irreducible $m\in A$ is called \emph{complementable} iff $\exists
\bar{m} \in A: m\meet\bar{m}=\bot \wedge m\join\bar{m}=\top$.  
%A complementable meet irreducible $\bar{M}$ of an abstract lattice $A$ is the complement of a meet 
%irreducible $M \in A$ such that $\bar{M} \in A$ and the concretisation of $M$ 
%is the set complement of $\bar{M}$.  
%If every meet irreducible in $A$ is complementable, then $A$ is said to
%be have complementable meet irreducibles.
\end{definition}

@@

\begin{definition}{(Meet Decomposition)} A meet decomposition of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$a=\bigscap_{m\in M} m$.
%$forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

@@

A meet decomposition of the outcome of abstract deduction transformer 
is obtained by taking a meet of the element $\langle y:[3, 5] \rangle, 
\langle x:[2, 4] \rangle \in ItvDom$ which gives set of meet irreducibles, 
$\{ \langle y \succeq 3 \rangle, \langle y \preceq 5 \rangle, 
\langle x \succeq 2 \rangle, \langle x \preceq 4 \rangle \}$, that are 
precisely complementable.

For a program with $N$ variables, let $L$ be the total number of 
meet irreducibles returned by a domain $D$.  For $D$ = {\em ItvDom}, the 
maximum value of $L$ is $2*N$, whereas the maximum value of $L$ is 
$2*(N^2)$ for $D$ = {\em OctDom}. Note that an octagon is the conjunction 
of all octagonal inequalities in the set $L$.
%
%========================
\input{literals-clauses}
%========================

>>>>

\begin{definition} 
A \emph{meet irreducible} $m$ 
in a complete lattice structure $A$ is an element with the following property.
\[\forall m_1, m_2 \in A: m_1 \meet m_2 = m \implies (m = m_1 \lor m = m_2), m \neq \top \]  
\end{definition}

@@

\begin{definition} 
A meet irreducible $m\in A$ is called \emph{complementable} iff $\exists
\bar{m} \in A: m\meet\bar{m}=\bot \wedge m\join\bar{m}=\top$.  
%A complementable meet irreducible $\bar{M}$ of an abstract lattice $A$ is the complement of a meet 
%irreducible $M \in A$ such that $\bar{M} \in A$ and the concretisation of $M$ 
%is the set complement of $\bar{M}$.  
%If every meet irreducible in $A$ is complementable, then $A$ is said to
%be have complementable meet irreducibles.
\end{definition}

@@

\begin{definition}
 A \emph{meet decomposition} of an abstract
element $a \in A$ is a set of meet irreducibles $M \subseteq A$ such that 
$a=\bigsqcap_{m\in M} m$.
%$forall m_i \in M, \meet(m_i) = a$, where $max(i) = |M|$.
\end{definition}

For example, the meet decomposition of the interval domain element
% $(x,y) \in [2,4]\times[3, 5]$ 
$2\leq x\leq 4 \wedge 3\leq y\leq 5$ is
the set $\{x\geq 2, x\leq 4, y\geq 3, y\leq 5\}$.
% \langle x:[2, 4] \rangle \in ItvDom$ which gives set of meet irreducibles, 
% $\{ \langle y \succeq 3 \rangle, \langle y \preceq 5 \rangle, 
% \langle x \succeq 2 \rangle, \langle x \preceq 4 \rangle \}$, that are 
% precisely complementable.

@@

% For a program with $N$ variables, let $L$ be the total number of 
% meet irreducibles returned by a domain $D$.  For $D$ = {\em ItvDom}, the 
% maximum value of $L$ is $2*N$, whereas the maximum value of $L$ is 
% $2*(N^2)$ for $D$ = {\em OctDom}. Note that an octagon is the conjunction 
% of all octagonal inequalities in the set $L$.
%
%========================
\input{literals-clauses}
%========================
